### 2018-08-23 analysis_code/agents_table.Rmd

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ht_lhr_3_arms_raw.csv", sep=""))

p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
priors <- as.list(unique(dat['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat['Warm.Start']))$Warm.Start, decreasing=FALSE)

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_longer_ws_raw.csv", sep=""))

p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000, 2000)
priors <- as.list(unique(dat['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat['Warm.Start']))$Warm.Start, decreasing=FALSE)

### 2018-08-23 analysis_code/tournament_table.Rmd

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_testing_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

>>>>

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ht_lhr_3_arms_raw.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_full_sim_no_rep_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat['Prior']))$Prior
